RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2022-12-07 main.tex
:pencil: Update scattering comparison

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communication}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communication}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}

@@

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of both coexisting links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
\end{abstract}

@@

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.
		Its applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		\gls{ambc} was then proposed in \cite{Liu2013b} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
		To tackle this, \cite{Yang2018} proposed cooperative \gls{ambc} where both primary (legacy) and backscatter links are decoded by the same receiver under various detection schemes.
		The concept was further refined as \gls{sr} illustrated in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides extra propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active transmission (if it exists) is influenced by the randomness of backscatter modulation.
		On the other hand, \gls{ris} in Fig. \ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses.
		The reflection pattern is deterministic over time that can be adaptively optimized and coordinated in real time.
		\gls{ris} recycles and redistributes the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.

		As illustrated in Fig. \ref{fg:scatter_illustration}, the scattering applications above involve either \emph{single active/passive link} or \emph{coexisting active and passive links}.
		In \gls{mbc}/\gls{bbc} (resp. \gls{ris}), the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal), where the detection for the only passive backscatter (resp. active primary) link can be coherent.
		On the other hand, \gls{ambc} and \gls{sr} simultaneously involve both links but the relationships in between are different.
		For \gls{ambc}, the primary system does not need to be aware of the backscatter system and both links are interfering each other.
		For \gls{sr}, both links are decoded by a co-located receiver such that cooperative transmission and reception become possible.
		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.

@@

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                                & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)                              & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Primary/Backscatter modulation                  & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
			Primary impact on backscatter detection         & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
			Scatterer impact on primary detection           & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperative transmission(s)                     & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
			Co-located receiver                             & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                               & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection                           & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern over time depends on         & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Reflection state (i.e. node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed                            & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
		\end{tabularx}
	\end{table*}

@@

		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the double modulation and signal characteristics of RIScatter without \gls{sic}.
		In active-passive coexisting networks, since the primary and backscatter messages are superimposed by multiplication and the backscatter symbol can be much longer than primary, the scattered signals from RIScatter nodes can be treated as (potentially random) multipath components during primary decoding, and the primary symbols can be viewed as a (potentially random) spreading code during backscatter decoding.
		Both randomness cannot be eliminated simultaneously by sequential decoding.
		Conventional \gls{sic}-based receiver that decodes from primary to backscatter link requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
		In contrast, the proposed practical receiver semi-coherently detects backscatter message from the accumulated receive energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel.
		It preserves simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol, and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.

>>>>

% glossaries-extra
\glsdisablehyper
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communication}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communication}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic \glsentryshort{bc}}
\newacronym{bbc}{BBC}{Bistatic \glsentryshort{bc}}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{MMSE}{Minimum Mean-Square-Error}
\newacronym{fpga}{FPGA}{Field-Programmable Gate Array}

@@

\begin{abstract}
	% \gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	% \gls{sr} incorporates a passive scatter node into existing radio networks to create additional propagation path and ride its own information towards the cooperative receiver.
	% \gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.
	\gls{bc} nodes harvest energy from and modulate information over an external electromagnetic wave.
	\gls{ris} adapts its phase shift response to enhance or attenuate channel strength in specific directions.
	In this paper, we show how those two seemingly different technologies (and their derivatives) can be unified to leverage their benefits simultaneously into a single architecture called RIScatter.
	RIScatter consists of multiple dispersed or co-located scatter nodes whose reflection states can be adapted to partially engineer the wireless channel of the existing link and partially modulate their own information onto the scattered wave.
	This contrasts with \gls{bc} (resp. \gls{ris}) where the reflection pattern is exclusively a function of the information symbol (resp. \gls{csi}).
	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the information source, \gls{csi}, and \gls{qos} of the active primary and passive backscatter links.
	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc} and \gls{ris}; boil down to either under specific input distribution; or evolve in a mixed form for heterogeneous traffic control and universal hardware design.
	For a single-user multi-node RIScatter network, we characterize the achievable primary-(total-)backscatter rate region by optimizing the input distribution at the nodes, the active beamforming at the \gls{ap}, and the backscatter detection regions at the user.
	% Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming via smart input distribution design, and the proposed practical receiver effectively accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transition between backscatter modulation and passive beamforming, and the proposed practical receiver accommodates the double modulation and signal characteristics in active-passive coexisting networks without \gls{sic}.
\end{abstract}

@@

\begin{section}{Introduction}
	\begin{subsection}{Fundamentals}
		\IEEEPARstart{F}{uture} wireless network is envisioned to provide high throughput, uniform coverage, pervasive connectivity, heterogeneous control, and cognitive intelligence for trillions of portable devices.
		As a mature low-power communication technique, \gls{bc} separates a conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} in Fig. \subref*{fg:mbc} and \gls{bbc} in Fig. \subref*{fg:bbc}.
		Relevant applications such as \gls{rfid} \cite{Dobkin2012,Landt2005} and passive sensor network \cite{Vannucci2008,Assimonis2016} have been extensively researched, standardized, and commercialized in the era of \gls{ioe}.
		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		To tackle this, \cite{Liu2013b} proposed \gls{ambc} where battery-free nodes recycle ambient signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connection in between.
		As shown in Fig. \subref*{fg:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but backscatter decoding is subject to the strong interference from the primary (legacy) link.
		Cooperative \gls{ambc} was then proposed where a co-located receiver decodes both active primary and passive backscatter links, where the rate and error performance are evaluated for various detection schemes \cite{Yang2018}.
		This concept was further refined by \cite{Liang2020} as \gls{sr} in Fig. \subref*{fg:sr} that cognitively incorporates \gls{ambc} with existing systems.
		In a \gls{sr} system, the active transmitter generates \gls{rf} wave carrying primary information, the passive node provides additional propagation path and ride its information over scattered signal, while the cooperative receiver jointly or sequentially decodes both links.
		Those \gls{bc} applications employ scatter nodes as pure information sources, and the active primary transmission (if it exists) can be influenced by the randomness of backscatter modulation.
		On the other hand, \gls{ris} in Fig. \ref{fg:ris} is a smart planar signal reflector that consists of numerous compact passive elements with adjustable amplitude and phase responses, whose reflection pattern over time is deterministic and optimized based on \gls{csi}.
		\gls{ris} smartly reflects the surrounding \gls{rf} waves to customize the wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
		In summary, \gls{mbc}/\gls{bbc} (resp. \gls{ris}) involves a \emph{single} passive backscatter (resp. active primary) link where the passive device modulates information (resp. enhances propagation) and the active device generates carrier wave (resp. modulated signal).
		% On the other hand, \gls{ambc} and \gls{sr} involve \emph{coexisting} active primary and passive backscatter links with different relationships in between.
		On the other hand, \gls{ambc} (resp. \gls{sr}) involves \emph{coexisting} active primary and passive backscatter links in a competitive (resp. collaborative) relationship.
		In \gls{ambc}, the backscatter link only needs to know the basic information (e.g., operating frequency and input distribution) of the primary link, and the primary link does not need to know the existence of the backscatter link.
		% In \gls{sr}, relevant \gls{csi} of both links should be available at the co-located receiver for cooperative decoding
		% In \gls{sr}, the co-located receiver needs to know the \gls{csi} of both links for cooperative decoding, and the primary transmitter may know
		In \gls{sr}, relevant \gls{csi} is exploited at the co-located receiver for cooperative decoding, and may also be exploited at the primary transmitter for cooperative active beamforming.
		A comparison of those scattering applications is summarized in Table \ref{tb:scattering_applications}.

@@

	% \begin{table*}[!t]
	% 	\caption{Comparison of Scattering Applications}
	% 	\label{tb:scattering_applications}
	% 	\rowcolors{2}{gray!25}{white}
	% 	\renewcommand{\arraystretch}{1.5}
	% 	\begin{tabularx}{\textwidth}{CCCCCC}
	% 		\toprule
	% 		\hiderowcolors
	% 		                                                & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
	% 		\showrowcolors
	% 		Coexisting link(s)                              & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
	% 		Primary/Backscatter modulation                  & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
	% 		Primary impact on backscatter detection         & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
	% 		Backscatter impact on primary detection         & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
	% 		Cooperative transmission(s)                     & ---                 & No                 & Primary transmitter (active beamforming)      & ---                 & Primary transmitter and scatter nodes                                   \\
	% 		Co-located receiver                             & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
	% 		Primary detection                               & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
	% 		Backscatter detection                           & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
	% 		Reflection pattern over time depends on         & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
	% 		Reflection state (i.e. node input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
	% 		Load-switching speed                            & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
	% 	\end{tabularx}
	% \end{table*}

	\begin{table*}[!t]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\rowcolors{2}{gray!25}{white}
		\renewcommand{\arraystretch}{1.5}
		\begin{tabularx}{\textwidth}{CCCCCC}
			\toprule
			\hiderowcolors
			                                                        & \gls{mbc}/\gls{bbc} & \gls{ambc}         & \gls{sr}                                      & \gls{ris}           & RIScatter                                                               \\ \midrule
			\showrowcolors
			Coexisting link(s)                                      & 1                   & 2 (competitive)    & 2 (collaborative)                             & 1                   & 2 (collaborative)                                                       \\
			Primary/Backscatter modulation                          & No/Yes              & Yes/Yes            & Yes/Yes                                       & Yes/No              & Yes/Yes                                                                 \\
			Primary impact on backscatter detection                 & Carrier             & Interference       & Spreading code                                & ---                 & Energy uncertainty                                                      \\
			Backscatter impact on primary detection                 & ---                 & Interference       & Channel uncertainty                           & Passive beamforming & Dynamic passive beamforming                                             \\
			Cooperation devices                                     & ---                 & No                 & Co-located receiver (and primary transmitter) & ---                 & Primary transmitter, scatter nodes, and co-located receiver             \\
			Cooperative decoding strategy                           & ---                 & No                 & Usually \gls{sic} from primary to backscatter & ---                 & No \gls{sic}, backscatter detection as part of primary channel training \\
			Primary detection                                       & ---                 & Semi-coherent      & Semi-coherent                                 & Coherent            & Coherent                                                                \\
			Backscatter detection                                   & Coherent            & Semi-coherent      & Coherent                                      & ---                 & Semi-coherent                                                           \\
			Reflection pattern over time depends on                 & Information source  & Information source & Information source                            & \gls{csi}           & Information source, \gls{csi}, and \gls{qos}                            \\
			Reflection state (i.e., backscatter input) distribution & Equiprobable        & Equiprobable       & Equiprobable or Gaussian                      & Degenerate          & Flexible                                                                \\
			Load-switching speed                                    & Fast                & Fast or slow       & Very slow                                     & Quasi-static        & Flexible                                                                \\ \bottomrule
		\end{tabularx}
	\end{table*}

	% ! cooperation:
	% - ambc: none
	% - sr: rx (possibly tx)
	% - riscatter: rx, tx, sx
	% ! csi, qos and backscatter constellation-aware input distribution + beamforming
	% ! csi and backscatter constellation-aware detection

@@

		\emph{Second,} we address the first challenge by proposing a practical receiver that effectively accommodates the double modulation and signal characteristics of RIScatter without \gls{sic}.
		In active-passive coexisting networks, since the primary and backscatter messages are superimposed by multiplication and the backscatter symbol can be much longer than primary, the scattered signals from RIScatter nodes can be treated as (potentially random) multipath components during primary decoding, and the primary symbols can be viewed as a (potentially random) spreading code during backscatter decoding.
		Both randomness cannot be eliminated simultaneously by sequential decoding.
		Conventional \gls{sic}-based receiver that decodes from primary to backscatter link requires $N$ re-encoding, precoding, subtraction together with a time-domain \gls{mrc} to decode each backscatter symbol.
		In contrast, the proposed practical receiver semi-coherently detects backscatter message from the accumulated receive energy, re-encodes to recover exact reflection patterns, and models the deterministic multipath within primary equivalent channel.
		The semi-coherent backscatter detection is indeed part of primary channel estimation.
		It preserves simultaneous backscatter modulation and dynamic passive beamforming by only one energy comparison, re-encoding, and precoding per backscatter symbol, and is suitable for arbitrary primary sampling rate and backscatter load-switching speed.
